Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Update mention of previous activity in the field

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, due to environmental concerns. \textbf{(Stojanovski, 2020)}

@@

>>>>

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities. Also the rise of investigation into self-propelled cars and carpools. The study of energy efficient mobility is only in its emerging phase. \textbf{(Stojanovski, 2020)}

@@

\bibitem{stojanovski-19}
%TODO
Stojanovski, T.
2019
Typo-morphology of transportation - Looking at historical development and multimodal futures of Swedish streets and roads
